\TheTitle

### 2017-07-05 paper/methodology.tex
Methodology: Removing tables answer tables

%TODO: Look at how to form research questions in LaTeX

We have two primary research questions;
\begin{enumerate}
  \item Is the DAG capable of providing the participants with an
    understanding of the repository events that are related to a commit?
  \item Does the \mt model make a difference in summarization tasks?
\end{enumerate}

@@

\subsection{Data Extraction}
\label{sub:data_extraction}

The study is recorded using screen capture and audio capture software
for further analysis. From the resulting videos, we are able to extract
the timing and accuracy of each participant over each task. We record
the timing, accuracy, task, commit, and tool used for each part. We also
record some addition information about whether the participant was
correct, guessing, partially correct, or completely wrong, as this may
provide some interesting insights.

The answers to each question is relatively straight-forward, as we can
extract the information directly from gitk and Linvis. Measuring the
accuracy of the questions is more challenging. In the question regarding
the merges leading to the merging of a given commit, both the merges and
the ordering of the merges matter. In the cases where the answer is not
a numerical value, we use the edit distance to determine the accuracy of
an answer. An edit distance of zero indicates a correct answer, while
any number other than zero indicates an incorrect answer. Adding,
reordering (where important), and removing commits or merges all incur a
penalty of 1 added to the edit distance.

The correct answers for \comA are shown in
Table~\ref{tab:coma_study_answers}, and the correct answers for \comB are
shown in Table~\ref{tab:comb_study_answers}.

\begin{table}[htpb]
  \centering
  \caption{Answers to the question from the conceptual and summarization portions of the user study for \comA}
  \label{tab:coma_study_answers}
  \begin{tabular}{l|l}
    Question                                              & Answer \\\hline\hline
    Number of commits in the merge tree                   & 1\\
    Number of merges in the merge tree                    & 1\\\hline
    Merges merging this commit into the master branch     & 1 (11df586407)\\
    Other commits that are merged in the same tree        & None\\
    How many authors are involved with this tree?         & 1\\
    Who contributed the most changes to this merge tree   & David\\
    How many files are modified in this merge tree        & 2\\
    Which file(s) had the most changes in this merge tree & both (pzl.c, asl.c)\\
    Which modules does this merge tree involve & wusb
  \end{tabular}
\end{table}

\begin{table}[htpb]
  \centering
  \caption{Answers to the question from the conceptual and summarization portions of the user study for \comB}
  \label{tab:comb_study_answers}
  \begin{tabular}{l|l}
    Question & Answer \\\hline\hline
    Number of commits in the merge tree & 5 \\
    Number of merges in the merge tree & 3\\\hline
    Merges merging this commit into the master branch     & (219b22b245
    \\
    & $\rightarrow$ \\
    & 8eb88c80d4)\\
    Other commits that are merged in the same tree        & ec4e86ba06\\
    & 9a3f371e99\\
    & 1c85cc6445\\
    & 7c2dfee848\\
    How many authors are involved with this tree?         & 4\\
    Who contributed the most changes to this merge tree   & Randy Dunlap\\
    How many files are modified in this merge tree        & 6\\
    Which file(s) had the most changes in this merge tree & pcm\_lib.c\\
    Which modules does this merge tree involve            & ALSA\\
  \end{tabular}
\end{table}

Extracting the timing information is prone to some issues with where the
duration of answering should start and stop. We try to eliminate these
issues by maintaining the following conventions; the answer duration
begins at the end of the last word of the prompt. The duration ends
immediately before the first word of the final modification to the
answer. Many answers are able to be answered in a single word or phrase,
but some may require multiple sentences that are broken by additional
processing by the participant. An Example of questions where the answer
may be interleaved with solving the task is the task asking the user to
provide the merges on the path from the commit into the master branch.
The goal of this is to eliminate the duration required to provide the
prompt, and eliminate the time required to provide the answer.

The information is then inserted into a sql database for further
analysis.

\subsection{Analysis}

As the goals of each section are different, the techniques for analyzing
the results are different. The conceptual questions are to demonstrate
the difficulty in comprehending the DAG model, so we simply provide the
metrics, showing how well the participants did in answering the
questions asked. The summarization tasks are meant for comparing the
ability of the participants to summarize two commits from the Linux
repository. As this is a comparison, further analysis is necessary to
determine the significance of our results. The final portion of the
study is designed to help us understand the group of users that we are
working with.

As the goals of the conceptual questions are to demonstrate the
difficulty in comprehending the DAG model, and determine how closely
users are able to make the mapping from the DAG to showing how a commit
was merged into the master branch, no further statistical analysis will
be performed on this data. We will provide the metrics response,
accuracy, and time metrics for these questions. No comparisons are made
between the models in these tasks, so no further analysis is necessary.

The summarization tasks are designed to compare the two models when the
participant is summarizing various aspects of the repository, including
the files modified and authorship information. We will use three terms
to describe the performance of a user; correctness, which indicates
simply whether the participant was correct or not, making no indication
toward how far from the correct answer they were; accuracy, indicating
how far from the correct answer the participant was; timing, which
indicates how long a participant took to answer the question. We begin
the analysis of these questions using the McNemar test, with $\alpha =
0.005$, measuring the correctness of the results provided by the
participant when using \tool versus gitk.
% TODO: cite the McNemar test maybe?
If the McNemar test indicates that we do not reject the null hypothesis,
we continue analyzing the difference in accuracy and timing metrics for
the merge-tree model versus the DAG.

For each test, we use a confidence level $\alpha = 0.005$, resulting in
a $\chi^2$ test statistic of 7.879.

% TODO: Add the null hypothesis and type of metrics analyzed for each summarization question

>>>>

We have two primary research questions;
\begin{RQ}
  \item

    Is the DAG capable of providing the users with an understanding of
    the repository events that are related to a commit?

  \item

    Does the \mt model make a difference in summarization tasks?

\end{RQ}

@@
